\documentclass[journal,12pt,twocolumn]{IEEEtran}

\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{txfonts}

\def\inputGnumericTable{}

\usepackage[latin1]{inputenc}
\usepackage{color}
\usepackage{array}
\usepackage{longtable}
\usepackage{calc}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{ifthen}
\usepackage{caption}
\captionsetup[table]{skip=3pt}
\providecommand{\pr}[1]{\ensuremath{\Pr\left(#1\right)}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\renewcommand{\thefigure}{\arabic{table}}
\renewcommand{\thetable}{\arabic{table}}
\title{Assignment 8 \\ \Large AI1110: Probability and Random Variables \\ \large Indian Institute of Technology Hyderabad}
\author{Rudransh Mishra \\ \normalsize AI21BTECH11025 \\ \vspace*{20pt} \normalsize  19 June 2022 \\ \vspace*{20pt} PROBABILITY, RANDOM VARIABLES, AND STOCHASTIC PROCESSES\\ \normalsize Athanasios Papoulis}

\begin{document}
% The title
\maketitle

% The question
\textbf{Example 15-2}

Consider a population that is able to produce new offspring of like kind. For each member let $p_k, k = 0, 1, 2,$ ... represent the probability of creating k new members. The direct descendents of the nth generation form the (n + 1 )st generation. The members of each generation are independent of each other. Suppose $X_n$ represents the size of the nth generation. It is clear that $X_n$ depends only on $X_n-1$ since $X_n = \sum_{i=1}^{x_n-1}Y_i$, where $Y_i$ represents the number of offspring of the i th member of the (n - 1) generation, and the manner in which the value of $X_n-1$ was reached is of no consequence. Thus $X_n$ represents a Markov chain.

Nuclear chain reactions, survival of family surnames, gene mutations, and waiting lines in a queueing system are all examples of branching processes. In a nuclear chain reaction, a particle such as a neutron scores a hit with probability p, creating m new particles, and $q = 1-p$ represents the probability that it remains inactive with no descendants. In that case, the only possible number of descendants is zero and m with probabilities q and p. If p is close to one, the number of particles is likely to increase indefinitely, leading to an explosion, whereas if P is close to zero the process may never start.

\begin{center} ---x-x-x-x-x-x--- \end{center}
\end{document}